FTLR proof cases

### 2018-06-11 fully-abstract-comp/ftlr-proof-cases.tex

In case \ref{case:ftlr:failed}, both executions go to failed. In this case, we
either assume that the target configuration terminates or that the source
configuration terminates, but in either case it leads to a contradiction with
the failing configuration.
\\\\
In case \ref{case:ftlr:halted}, both source and target configuration halts in 0
steps, so both directions of $\lro$ are trivially satisfied.
\\\\
In case \ref{case:ftlr:get-and-arith-op}, we use the induction hypothesis to get
\[
  \npair[n'-1]{(((\perm,\lin),\baddr,\eaddr,\aaddr+1),((\perm,\lin),\baddr,\eaddr,\aaddr+1))} \in \lre(W)
\]
This is possible by using the initial assumptions along with Lemma \ref{lem:downwards-closed}.
By Lemma~\ref{lem:downwards-closed}, we know $\memSat[n'-1]{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$.
By Lemma~\ref{lem:downwards-closed} and the fact that integers are always safe,
we know $\npair[n'-1]{(\reg_S\update{r}{z},\reg_T\update{r}{z})} \in \lrr(W_R)$.
This allows us to conclude
\[
  \npair[n'-1]{(\Phi_S',\Phi_T')} \in \lro
\]
as desired.
\\\\
In case \ref{case:ftlr:call}, we first need to let the target execution catch
up. That is $\Phi_T' \nstep[15]{} \Phi_T''$ for 
\[
\Phi_T'' = \Phi_T
\begin{array}[t]{l}
  \update{\mem.\aaddr_\stk}{42} \\
  \updReg{\rstk}{((\rw,\linear),\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1)} \\
  \updReg{\rretd}{\sealed{\sigma',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1)}} \\
  \updReg{\rretc}{\sealed{\sigma',((\perm,\lin),\baddr,\eaddr,\aaddr+\var{off\_return})}} \\
  \updReg{\rtmp{1}}{0}\\
  \updReg{r_1,r_2}{\linCons{\Phi_T(r_1)},\linCons{\Phi_T(r_2)}}\\
  \updReg{\pcreg}{c_1'}\\
  \updReg{\rdata}{c_2'}
\end{array}
\]
where $\Phi_T(r_i) = \sealed{\sigma,c_i'} \text{ for $i\in\{1,2\}$}$ and $\var{off\_return} = 15$ which is the offset to the return code.
Now using Lemma~\ref{lem:lro-anti-red-gen} again, it suffices to show
\[
  \npair[n'-1]{(\Phi_S',\Phi_T'')} \in \lro
\]
By assumption, we have $\npair[n']{(\reg_S(r_i),\reg_T(r_i))} \in \lrr(W_{R,i})$ for some $W_{R,i}$ with $i \in \{1,2\}$.
We know the capabilities in $r_1$ and $r_2$ are sealed capabilities, and by
Lemma~\ref{lem:unique-h-sigma} and the definition of $\lrv$ we get
$\npair[n'-1]{\stpair[.]{c_2}{c_2'}} \in H_\sigma \; \sigma \; \xi^{-1}(W_{R,2})$
and w.l.o.g.\

@@

we split the world in the same way for the registers that remain unchanged, the
result follows from Lemma \ref{lem:downwards-closed} and \ref{lem:monotonicity}.
This leaves the following cases:
\begin{description}
\item[Case $\rstk$:] \lau{TODO}
\item[Case $\rtmp{1}$:] \lau{TODO}
\item[Case $r_1$,$r_2$:] \lau{TODO}
\item[Case $\rretd$:] We have to show 
  \[
    \npair[n'-1]{(\sealed{\sigma',\retptrd(\aaddr_\stk,\eaddr_\stk)},\sealed{\sigma',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1)})} \in \lrv(W_{R,\rretd}')
  \]
  where $W_{R,\rretd}'$ is the part of $W_R'$ with ownership over $r_\var{priv\_stk}$.
  From the assumption $\npair{[\baddr,\eaddr]} \in \xReadCond{W}$ we get $R \subseteq \addressable{\normal, \pwheap}$ and $\exists M : S \fun \powerset{\MemSeg}$ such that $\biguplus_{r\in S} \dom(M(r)) \supseteq [\baddr,\eaddr]$ and $\forall r \in S \ldotp \pwheap(r) \nequal \codereg{\_,\_,M(r),\gc}$.
  Further by $\memSat[n']{\ms_S,\stk,\ms_\stk,\ms_T}{W}$, we know that for one
  $r \in S$ there is a $\mscode' \subseteq \mscode$\footnote{Follows from
    $H^\var{code}$ requiring $\dom(\mscode') \subseteq \ta$ and $\dom(\mscode) =
    \ta$ and finally that $\mscode$ is part of $\ms_S$.} such that
  \begin{equation}
    \npair[n']{(\mscode',\mscode')} \in H^{\var{code}} \; \sigrets' \; \sigcloss' \; \mscode' \; (\ta,\_)\label{eq:ftlr:rretd:Hcode}
  \end{equation}
 where $\sigma' \in \sigrets'$ and $\dom(\mscode') \supseteq [\baddr,\eaddr]$ and $\aaddr + \offpc \in \dom(\mscode')$.
  That is $\mscode'$ contains the call we are considering.
  \lau{TODO: Make the above more precise and possibly put into a lemma.}
  Use the $r$ in question as the witness. We now have to show:
  \begin{enumerate}[label=\alph*)]
  \item for $n'' < n'-1$ we have
    \[\npair[n'']{\left(\array{l}\retptrd(\aaddr_\stk,\eaddr_\stk),\\((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1)\endarray\right)}
      \in H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode'
      \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_{R,\rretd}')
    \]
    First $\dom(\mscode') \subseteq \ta$ follows from \ref{eq:ftlr:rretd:Hcode} and the assumption $[\baddr,\eaddr] \ subseteq \ta$.
    Now pick $r_\var{priv\_stk}$ as the witness.
    We immediately get $\dom(\ms_{\stk\_\priv,S}) = \dom(\Phi_T''.\mem|_{[\aaddr_\stk,\eaddr_\stk]}) = [\aaddr_\stk,\eaddr_\stk]$.
    Next, $\decInstr(\mscode'(\aaddr,\aaddr+\calllen-1)) = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}}$ follows from $\callCond{\Phi_S,r_1,r_2,\aaddr}$.
    Finally, $\ms_\code(\aaddr+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr}$ with $\sigma' = \sigma_\baddr + \offpc \in \sigrets'$ which follows from $\sigrets',\sigcloss' \vdash_{\mathrm{comp-code}} \mscode'$ and the fact that the call is there.
  \item $\isLinear{\sealed{\sigma',\retptrd(\aaddr_\stk,\eaddr_\stk)}}$ iff
    $\isLinear{\sealed{\sigma',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk)}}$\\
    Trivial as both are linear.    
  \item
    \[
      \begin{array}{l}
        \forall W'' \future \purePart{W_{R,\rretd}'}, W_o, n'' < n'-1,\\
        \quad\npair[n'']{(\vsc_S',\vsc_T')}
        \in  H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode'
        \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_o) \ldotp \\
        \qquad\npair[n']{\retptrd(\aaddr_\stk,\eaddr_\stk),\vsc_S',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1),\vsc_T'} \in
        \lrexj(W'\oplus W_o))
      \end{array}
    \]
    Trivial as both configuration fails.
  \end{enumerate}

\item[Case $\rretc$:] \lau{TODO}
\end{description}

@@

\begin{lemma}

  If $\npair{[\baddr,\eaddr]} \in \xReadCond{W}$ and
  $\memSat{\ms_S \uplus \mscode, \stk,\ms_\stk,\ms_T}{W}$
  $[\baddr,\eaddr] \subseteq \dom(\mscode)$ and
  \[
    \begin{array}{l}
      \exists r \in \dom(\pwheap) ,\mscode' \ldotp \\
      \quad \pwheap(r) = \codereg{\sigrets',\sigcloss',\mscode',(\ta,\stkb)} \text{ and } \\
      \quad [\baddr,\eaddr] \subseteq \dom(\mscode') \text{ and } \\
      \quad \sigma \in \sigrets' \subseteq \sigrets \text{ and } \\
      \quad \sigclos \subseteq \sigclos'
    \end{array}
  \]
\end{lemma}

@@

%%% Local Variables:
%%% TeX-master: "technical-report"
%%% End:

>>>>

In case \ref{case:ftlr:failed}, both executions go to failed. In this case, we
either assume that the target configuration terminates or that the source
configuration terminates, but in either case it leads to a contradiction with
the failing configuration.
\\\\
In case \ref{case:ftlr:halted}, both source and target configuration halts in 0
steps, so both directions of $\lro$ are trivially satisfied.
\\\\
In case \ref{case:ftlr:get-and-arith-op}, we use the induction hypothesis to get
\[
  \npair[n'-1]{(((\perm,\lin),\baddr,\eaddr,\aaddr+1),((\perm,\lin),\baddr,\eaddr,\aaddr+1))} \in \lre(W)
\]
This is possible by using the initial assumptions along with Lemma \ref{lem:downwards-closed}.
By Lemma~\ref{lem:downwards-closed}, we know $\memSat[n'-1]{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$.
By Lemma~\ref{lem:downwards-closed} and the fact that integers are always safe,
we know $\npair[n'-1]{(\reg_S\update{r}{z},\reg_T\update{r}{z})} \in \lrr(W_R)$.
This allows us to conclude
\[
  \npair[n'-1]{(\Phi_S',\Phi_T')} \in \lro
\]
as desired.
\\\\
In case \ref{case:ftlr:call}, we first need to let the target execution catch
up. That is $\Phi_T' \nstep[15]{} \Phi_T''$ for 
\[
\Phi_T'' = \Phi_T
\begin{array}[t]{l}
  \update{\mem.\aaddr_\stk}{42} \\
  \updReg{\rstk}{((\rw,\linear),\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1)} \\
  \updReg{\rretd}{\sealed{\sigma',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1)}} \\
  \updReg{\rretc}{\sealed{\sigma',((\perm,\lin),\baddr,\eaddr,\aaddr+\retoffset)}} \\
  \updReg{\rtmp{1}}{0}\\
  \updReg{r_1,r_2}{\linCons{\Phi_T(r_1)},\linCons{\Phi_T(r_2)}}\\
  \updReg{\pcreg}{c_1'}\\
  \updReg{\rdata}{c_2'}
\end{array}
\]
where $\Phi_T(r_i) = \sealed{\sigma,c_i'} \text{ for $i\in\{1,2\}$}$ and $\retoffset = 15$ which is the offset to the return code.
Now using Lemma~\ref{lem:lro-anti-red-gen} again, it suffices to show
\[
  \npair[n'-1]{(\Phi_S',\Phi_T'')} \in \lro
\]
By assumption, we have $\npair[n']{(\reg_S(r_i),\reg_T(r_i))} \in \lrr(W_{R,i})$ for some $W_{R,i}$ with $i \in \{1,2\}$.
We know the capabilities in $r_1$ and $r_2$ are sealed capabilities, and by
Lemma~\ref{lem:unique-h-sigma} and the definition of $\lrv$ we get
$\npair[n'-1]{\stpair[.]{c_2}{c_2'}} \in H_\sigma \; \sigma \; \xi^{-1}(W_{R,2})$
and w.l.o.g.\

@@

we split the world in the same way for the registers that remain unchanged, the
result follows from Lemma \ref{lem:downwards-closed} and \ref{lem:monotonicity}.
This leaves the following cases:
\begin{description}
\item[Case $\rstk$:] \lau{TODO}
\item[Case $\rtmp{1}$:] \lau{TODO}
\item[Case $r_1$,$r_2$:] \lau{TODO}
\item[Case $\rretd$:] We have to show 
  \[
    \npair[n'-1]{(\sealed{\sigma',\retptrd(\aaddr_\stk,\eaddr_\stk)},\sealed{\sigma',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1)})} \in \lrv(W_{R,\rretd}')
  \]
  where $W_{R,\rretd}'$ is the part of $W_R'$ with ownership over $r_\var{priv\_stk}$.
  From the assumption $\npair{[\baddr,\eaddr]} \in \xReadCond{W}$ we get $R \subseteq \addressable{\normal, \pwheap}$ and $\exists M : S \fun \powerset{\MemSeg}$ such that $\biguplus_{r\in S} \dom(M(r)) \supseteq [\baddr,\eaddr]$ and $\forall r \in S \ldotp \pwheap(r) \nequal \codereg{\sigrets',\_,M(r),\gc}$.
  Further by $\memSat[n']{\ms_S,\stk,\ms_\stk,\ms_T}{W}$, we know that for one
  $r \in S$ there is a $\mscode' \subseteq \mscode$\footnote{Follows from
    $H^\var{code}$ requiring $\dom(\mscode') \subseteq \ta$ and $\dom(\mscode) =
    \ta$ and finally that $\mscode$ is part of $\ms_S$.} such that
  \begin{equation}
    \npair[n']{(\mscode',\mscode')} \in H^{\var{code}} \; \sigrets' \; \sigcloss' \; \mscode' \; (\ta,\_)\label{eq:ftlr:rretd:Hcode}
  \end{equation}
  where $\sigma' \in \sigrets'$ and $\dom(\mscode') \supseteq [\baddr,\eaddr]$ and $\aaddr + \offpc \in \dom(\mscode')$.
  That is $\mscode'$ contains the call we are considering.
  \lau{TODO: Make the above more precise and possibly put into a lemma (also needed in the next case).}
  Use the $r$ in question as the witness.
  The $\xReadCond{}$ gives us $\pwheap(r) \nequal \codereg{\_,\_,\mscode',\gc}$.
  As it is a pure region, it is also present in the future world we consider.
  We now have to show:
  \begin{enumerate}[label=\alph*)]
  \item for $n'' < n'-1$ we have
    \[\npair[n'']{\left(\array{l}\retptrd(\aaddr_\stk,\eaddr_\stk),\\((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1)\endarray\right)}
      \in H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode'
      \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_{R,\rretd}')
    \]
    First $\dom(\mscode') \subseteq \ta$ follows from \ref{eq:ftlr:rretd:Hcode} and the assumption $[\baddr,\eaddr] \ subseteq \ta$.
    Now pick $r_\var{priv\_stk}$ as the witness.
    We immediately get $\dom(\ms_{\stk\_\priv,S}) = \dom(\Phi_T''.\mem|_{[\aaddr_\stk,\eaddr_\stk]}) = [\aaddr_\stk,\eaddr_\stk]$.
    Next, $\decInstr(\mscode'(\aaddr,\aaddr+\calllen-1)) = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}}$ follows from $\callCond{\Phi_S,r_1,r_2,\aaddr}$.
    Finally, $\ms_\code(\aaddr+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr}$ with $\sigma' = \sigma_\baddr + \offpc \in \sigrets'$ which follows from $\sigrets',\sigcloss' \vdash_{\mathrm{comp-code}} \mscode'$ and the fact that the call is there.
  \item $\isLinear{\sealed{\sigma',\retptrd(\aaddr_\stk,\eaddr_\stk)}}$ iff
    $\isLinear{\sealed{\sigma',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk)}}$\\
    Trivial as both are linear.    
  \item
    \[
      \begin{array}{l}
        \forall W'' \future \purePart{W_{R,\rretd}'}, W_o, n'' < n'-1,\\
        \quad\npair[n'']{(\vsc_S',\vsc_T')}
        \in  H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode'
        \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_o) \ldotp \\
        \qquad\npair[n']{\retptrd(\aaddr_\stk,\eaddr_\stk),\vsc_S',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1),\vsc_T'} \in
        \lrexj(W'\oplus W_o))
      \end{array}
    \]
    Trivial as both configuration fails.
  \end{enumerate}

\item[Case $\rretc$:]
  We have to show 
  \[
    \npair[n'-1]{\left(\array{l}\sealed{\sigma',\retptrc(\baddr,\eaddr,\aaddr +
        \calllen)},\\\sealed{\sigma',((\rx,\normal),\baddr,\eaddr,\aaddr + \retoffset)}\endarray\right)} \in \lrv(W_{R,\rretc}')
  \]
  where $W_{R,\rretc}'$ has the ownership of $W$.
  Just as in the previous case, we know that for some region $r$ there exists $\mscode' \subseteq \mscode$ such that: $\pwheap(r) \nequal \codereg{\sigrets',\_,\mscode',\gc}$ where $\sigma' \in \sigrets'$ and $\dom(\mscode') \supseteq [\baddr,\eaddr]$ and $\aaddr + \offpc \in \dom(\mscode')$.
  It follows easily from the definition of $H_\sigma^\var{code}$ that
  \begin{equation}
    \label{eq:code-caps-in-h-sigma}
    \npair[n'']{\left(\array{l}\retptrc(\baddr,\eaddr,\aaddr + \calllen),\\((\rx,\normal),\baddr,\eaddr,\aaddr + \retoffset)\endarray\right)} \in H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode' \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_{R,\rretc}')
  \end{equation}
  for $n'' < n'-1$.
  Both capabilities are non-linear, so $\isLinear{\retptrc(\baddr,\eaddr,\aaddr + \calllen)}$ iff $\isLinear{((\rx,\normal),\baddr,\eaddr,\aaddr + \retoffset)}$ is indeed the case.
  Finally we need to show:
  \[
    \begin{array}{l}
      \forall W'' \future \purePart{W_{R,\rretc}'}, W_o, n'' < n'-1,\\
      \quad  \npair[n'']{(\vsc_S',\vsc'_T)} \in H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode' \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_o) \ldotp \\
      \qquad \npair[n'']{\retptrc(\baddr,\eaddr,\aaddr + \calllen),\vsc_S',((\rx,\normal),\baddr,\eaddr,\aaddr + \retoffset),\vsc_T'} \in \lrexj(W''\oplus W_o))
    \end{array}
  \]
  To this end let $W'' \future \purePart{W_{R,\rretc}'}$ and $W_o$ be given s.t.
  $W'' \future \purePart{W_{R,\rretc}'} \oplus W_o$ is defined. Further, let
  $\npair[n'']{(\vsc_S',\vsc'_T)} \in H^\mathrm{code,\square}_\sigma \;
  \sigrets' \; \sigcloss' \; \mscode' \; (\ta,\stkb) \; \sigma' \;
  \xi^{-1}(W_o)$ be given and show 
  \[
    \npair[n'']{\retptrc(\baddr,\eaddr,\aaddr + \calllen),\vsc_S',((\rx,\normal),\baddr,\eaddr,\aaddr + \retoffset),\vsc_T'} \in \lrexj(W''\oplus W_o))
  \]
  Now let $n''' \leq n''$ be given along with $\reg[3]_S$, $\reg[3]_T$, $\ms^{(3)}_S$, $\ms^{(3)}_T$,$\ms^{(3)}_\stk$, $\stk^{(3)}$, $W_R''$, and $W_M''$ such that
  \begin{itemize}
  \item $W'' \oplus W_o \oplus W_R'' \oplus W_M''$ is defined
  \item $\memSat[n''']{\ms^{(3)}_S,\ms^{(3)}_\stk, \stk^{(3)}, \ms^{(3)}_T}{W_M''}$
  \item $\npair[n''']{(\reg[3]_S,\reg[3]_T)} \in \lrr(W_R'')$
  \end{itemize}

  Based on $H_\sigma^\var{code}$, there are three possible values for $\vsc_S'$ and $\vsc_T'$.
  In the first case, $\vsc_S'$ is a $\retptrc$ and $\vsc_T'$ is a capability with permission $\rx$.
  In this case, $\xjumpResult{}{}{}$ will give to failed configurations which is trivially in the observation relation.
  In the next case, it is required that $\sigma' \in \sigcloss'$, but this cannot be the case as \lau{TODO I think this case should follow from $H^\var{code}$ and the comp-code judgement, but it does not.
    Specifically, the comp-code judgement (for now) does not require $\sigrets'$ and $\sigcloss'$ to be disjointed.}

  This leaves us with one final case, namely $\vsc_S'= \retptrd(\baddr_\stk',\eaddr_\stk')$ and $\vsc_T'=((\rw,\linear),\baddr_\stk',\eaddr_\stk',\baddr_\stk'-1)$.
  Further we know
  \[
    \begin{array}{l}
    \exists r \in \addressable{\linear,\pwpriv[W_o]} \ldotp \pwpriv[W_o](r).H \nequal (\stareg[(\ms_{\priv,S}^{(3)},\ms_{\priv,T}^{(3)}),(\ta,\stkb)]{\spao,\square}, \aaddr'+\calllen) \tand \\
    \quad \dom(\ms_S) = \dom(\ms_T) = [\baddr_\stk',\eaddr_\stk'] \tand\\
    \quad \decInstr{\code([\aaddr',\aaddr' + \calllen-1])} = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}} \tand \\
    \quad \code(\aaddr'+\offpc) = \seal{\sigma_b,\sigma_e,\sigma_b} \tand \sigma = \sigma_b + \offsigma \in \sigrets 
    \end{array}
  \]
  Call this region $r'$.
  By the above, the fact that the code capability pair is in $H_\sigma^\var{code}$ (\ref{eq:code-caps-in-h-sigma}) and Lemma~\ref{lem:unique-ret-seals}, we get $\aaddr' = \aaddr$.
  This means that $W_M''$ and $W_R''$ has this region.

  We know that the two register-files are related which in particular means that
  the values in register $\rstk$ are related. Now consider the following cases:
  \lau{TODO: Perhaps make a lemma that says if source fail and target step to
    fail, then the two configurations are in $\lro$.}
  \item $\Phi_S(\rstk) \neq \stkptr{\_,\_,\_,\_}$\\
    In this case due to $\reg[3]_S$ being related to $\reg[3]_T$, there are three cases we need to consider.
    In all cases, the source configuration will fail because the value in the stack register is not a stack capability.
    If we can argue that the target configuration also will fail, then the two are in the observation relation.
    First, if $\reg[3]_T = \sealed{\sigma_\var{ret\_\stk},\vsc_T''}$, then the return code will fail when the base address (a sealed capability has no base address, so the instruction returns $-1$) is compared to $\stkb$.
    Second, if $\reg[3]_T = \seal{\_,\_,\_}$, then the target execution fails when it attempts to splice this seal with $\vsc_T'$.
    Finally, $\reg[3]_T = ((\perm_\var{ret\_\stk},\lin_\var{ret\_\stk}),\baddr_\var{ret\_\stk},\eaddr_\var{ret\_\stk},\_)$ and $\npair[n''']{[\baddr_\var{ret\_\stk},\eaddr_\var{ret\_\stk}]} \in \readCond{\lin_\var{ret\_\stk},W_{R,\rstk}''}$ is satisfied.
    This means that it is satisfied by some heap region, but by the memory satisfaction assumption $\stkb$ must be in the free stack part of the world.
    This means that the execution will fail that $\stkb$ check.
  \item $\Phi_S(\rstk) = \stkptr{\perm_\var{ret\_\stk},\baddr_\var{ret\_\stk},\_,\_}$ and $\baddr_\var{ret\_\stk} \neq \stkb$\\
    Here the source side will fail the xjmp as the base address is not $\stkb$.
    Similarly on the target side, the return code will fail the $\stkb$ check.
  \item $\Phi_S(\rstk) = \stkptr{\_,\baddr_\var{ret\_\stk},\eaddr_\var{ret\_\stk},\_}$ and $\baddr_\var{ret\_\stk} = \stkb$ and either $\eaddr_\var{ret\_\stk} +1 \neq \baddr_\stk' $ or $\perm_\var{ret\_\stk} \neq \rw$ or
    $\baddr_\var{ret\_\stk} > \eaddr_\var{ret\_\stk}$.\\
    In this case, the source configuration will fail as one of the conditions in $\var{xjumpResult}$ will not be met.
    On the target side, the splice will fail as either the two capabilities being spliced don't line up, the permissions don't match, or the range of authority is empty, respectively.
  \item $\Phi_S(\rstk) = \stkptr{\perm_\var{ret\_\stk},\baddr_\var{ret\_\stk},\eaddr_\var{ret\_\stk},\_}$ and $\baddr_\var{ret\_\stk} = \stkb$ and $\eaddr_\var{ret\_\stk} +1 = \baddr_\stk' $ and $\perm_\var{ret\_\stk} = \rw$ and $\baddr_\var{ret\_\stk} \leq \eaddr_\var{ret\_\stk}$.
    \\
    We would like to show that $\ms_{\priv,S}^{(3)}$ is the top most stack frame and that $r'$ governs it.
    By the memory satisfaction assumption and the presence of $r'$ in $W_M''$ we know that $\stk^{(3)}$ is non-empty.
    By the memory satisfaction on the private stack, the following must be the case:
      \begin{array}{l}
        \stk^{(3)} = (\opc_0,\ms_0), \dots (\opc_m,\ms_m) \wedge \\
        \forall i \in \{0,\dots,m\} \ldotp (\dom(\ms_i) \neq \emptyset \wedge\\
        \quad \forall i < j \ldotp \forall a \in \dom(\ms_i) \ldotp \forall a' \in \dom(\ms_j) \ldotp \stkb < a < a')\\
      \end{array}
    Assume for contradiction $\ms_{\priv,S}^{(3)}$ is not the top frame. In that
    case $\dom(\ms_0) \neq \emptyset$ and $\forall a \in \dom(\ms_0) \ldotp
    \ldotp \stkb < a < b_\stk$ at the same time, we know
      \npair[n'']{(\stkptr{\rw,\stkb,\eaddr_\var{ret\_\stk},\_},((\rw,\linear),\stkb,\eaddr_\var{ret\_\stk},\_))}
      \in \lrv(W_{R,\rstk}'')
    which means that the free stack part of the world contains a region that at least governs $[\stkb,\eaddr_\var{ret\_\stk}]$.
    Combine this with $\eaddr_\var{ret\_\stk} +1 = \baddr_\stk' $, we can conclude that no such address can exist in $\ms_0$, so it must be empty, but this cannot be the case either.
    Therefore, the top stack frame must contain $\ms_{\priv,S}^{(3)}$.
    Further, due to the disjointedness required by memory satisfaction, it must be $r'$ that governs this stack frame.
    This also means that we have $\opc_0 =  \aaddr+\calllen$.
    With this, we have all the requirements for $\var{xjumpResult}$ satisfied on
    both sides which allows us to pick the necessary configurations:
    \begin{multline*}
      \Phi^{(4)}_S=\xjumpResult{r_1}{r_2}{(\ms_S^{(3)},\reg[3]_S,(\ms_{\priv,S}^{(3)},\aaddr+\calllen)
        :: \stk^{(3)}_\var{rest},\ms_\stk^{(3)})} =\\
      (\ms_S^{(3)},\reg[3]_S
      \arraycolsep=0pt
      \begin{array}[t]{l}
        \updReg{\pcreg}{((\rx,\normal),\baddr,\eaddr,\aaddr+\calllen)} \\
        \updReg{\rdata}{0} \\
        \updReg{\rstk}{\stkptr{\rw,\stkb,e_\stk',\eaddr_\var{ret\_stk}+1}} \\
        \updReg{\rtmp{1}}{0} \\
        \updReg{\rtmp{2}}{0}
      \end{array}
      ,\stk^{(3)}_\var{rest},\ms_{\priv,S}^{(3)} \uplus \ms_\stk^{(3)})
    \end{multline*}
    \begin{multline*}
      \Phi^{(4)}_T=\xjumpResult{r_1}{r_2}{(\ms_T^{(3)},\reg[3]_T)} =\\
      (\ms_T^{(3)},\reg[3]_S
      \arraycolsep=0pt
      \begin{array}[t]{l}
        \updReg{\pcreg}{((\rx,\normal),\baddr,\eaddr,\aaddr+\retoffset)} \\
        \updReg{\rdata}{((\rw,\linear),\stkb,\eaddr_\var{ret\_stk})}
      \end{array})
    \end{multline*}
    It now remains to show
      \npair[n''']{(\Phi^{(4)}_S,\Phi^{(4)}_T)} \in \lro
    Use Lemma~\ref{lem:lro-anti-red-gen} by which it suffices to show the
    following two things:
    \item
        \Phi^{(4)}_T \step[l] \Phi^{(5)}_T = (\ms_T^{(3)},\reg[3]_S
        \arraycolsep=0pt
        \begin{array}[t]{l}
          \updReg{\pcreg}{((\rx,\normal),\baddr,\eaddr,\aaddr+\calllen)} \\
          \updReg{\rdata}{0} \\
          \updReg{\rstk}{((\rw,\linear),\stkb,e_\stk',\eaddr_\var{ret\_stk}+1)} \\
          \updReg{\rtmp{1}}{0} \\
          \updReg{\rtmp{2}}{0}
        \end{array})
      for some number of steps $l$. This follows immediately from the
      operational semantics.
    \item
        \npair[n''']{(\Phi^{(4)}_S,\Phi^{(5)}_T)} \in \lro
      Here we need to use the induction hypothesis.

\end{description}
This concludes case \ref{case:ftlr:scall:reg}

@@

@@

\begin{lemma}[Unique return seals]
  \label{lem:unique-ret-seals}
  If
  \begin{itemize}
  \item $\mscode([\aaddr..\aaddr+\calllen-1]) = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}}$
  \item $\mscode([\aaddr'..\aaddr'+\calllen-1]) = \overline{\scall{\offpc',\offsigma'}{r_1'}{r_2'}}$
  \item $\mscode(\aaddr + \offpc) = \seal{\sigma_b,\sigma_e,\sigma_b}$ and $\sigma = \sigma_b + \offpc$
  \item $\mscode(\aaddr' + \offpc') = \seal{\sigma_b',\sigma_e',\sigma_b'}$ and $\sigma = \sigma_b' + \offpc'$
  \end{itemize}
  then
  \[
    \aaddr = \aaddr'
  \]
  and $\offpc = \offpc'$ and $\offsigma = \offsigma'$ and $r_1 = r_1'$ and $r_2 = r_2'$ and $\sigma_b = \sigma_b'$ and $\sigma_e = \sigma_e'$.
\end{lemma}
\begin{proof}
  \lau{TODO}
\end{proof}
%%% Local Variables:
%%% TeX-master: "technical-report"
%%% End:
